---
title: "Prediction Intervals for Electricy Load Forecasting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 7,
  fig.height = 5,
  comment = "#>"
)

library(AdaptiveConformal)

```

In this vignette, we will produce conformal prediction intervals for French electricity demand data from the [`opera`](https://cran.r-project.org/web/packages/opera/index.html) package.

```{r load_data}
data(electric_load, package = "opera")
```

The dataset comprise weekly observations of total electricity consumption in France from 1996 to 2009. 
```{r extract_Y}
Y <- ts(electric_load$Load, frequency = 52, start = 1996)
```

```{r plot_Y}
plot(Y, ylab = "Electricity consumption")
```

Let $Y_t$ be the electricity demand at time $t$ for $t = 1, \dots, T$. 

We generate predictions and prediction intervals in the following procedure. Set $t^* \geq 1$ to the first year in which predictions will be generated.

- For $t = t^*, \dots, T$:
  - Train a result $\mathcal{M}_t$ to predict $Y_t$ using only the data $Y_1, \dots, Y_{t-1}$.
  - Generate a prediction $\hat{Y}_t$ using $\mathcal{M}_t$.
  - Generate a predictive interval $[\hat{Y}_t^l, \hat{Y}_t^u]$ using an ACI algorithm.
  - Observe the true observation $Y_t$ and update the ACI algorithm accordingly. 

## Predictions
For this vignette, we'll train the results first as an initial step and then apply several ACI methods as a second step. As a predictive method we will use [SARIMA](https://en.wikipedia.org/wiki/Autoregressive_integrated_moving_average) as implemented in the `forecast::auto.arima` function. We start predicting the weekly electricity load at at $t^* = 350$ so that the SARIMA model has enough data to work with.

```{r predictions, cache = TRUE}
predictions <- rep(NA, length(Y))
t_star <- 350
for(t in t_star:length(Y)) {
  # Fit a SARIMA result 
  fit <- forecast::Arima(
    window(Y, end = time(Y)[t - 1]), 
    order = c(1, 0, 0), 
    seasonal = c(1, 1, 0)
  )
  
  # Get prediction of next Y
  predictions[t] <- forecast::forecast(fit, h = 1)$mean
}
```

Here is what the one-step-ahead predictions look like compared to the observed data.
```{r plot_predictions}
plot(Y, ylab = "Electricity consumption")
lines(ts(predictions, frequency = 52, start = 1996), col = "red")
legend("topleft", legend = c("Observations", "Predictions"), fill = c("black", "red"))
```

## Conformal Prediction Intervals
We start by initializing the ACI object, targeting $\alpha = 90\%$ prediction intervals. The first method we will apply is the `AgACI` method. This method requires specifying a grid of learning rates to use to generate candidate prediction intervals. The candidate intervals are then combined using an online expert aggregation method.
```{r initialize_agaci}
result <- aci(method = "AgACI", alpha = 0.9)
```

Next, we update the ACI method with the online predictions and observed data.
```{r update_agaci}
result <- update(result, newY = Y[t_star:length(Y)], newpredictions = predictions[t_star:length(Y)])
```

Note that we could also build the result by supplying the observations one at a time, which may be useful in a true online or streaming scenario where we receive the observations sequentially.
```{r initialize_and_update_agaci_iteratively}
result <- aci(method = "AgACI", alpha = 0.9)
for(t in t_star:length(Y)) {
  result <- update(result, newY = Y[t], newpredictions = predictions[t])
}
```

We can print a summary to see some basic information about the results, including the empirical coverage and mean interval width.
```{r agaci_summary}
summary(result)
```

We can also plot the observations and the conformal prediction intervals.
```{r agaci_plot}
plot(result)
```

Let's zoom in on a smaller section so we can see the prediction intervals more clearly:
```{r agaci_plot_zoom}
plot(result, index = 200:300)
```

Next, we can try a different ACI method: Fully Adaptive Conformal Inference (DtACI). We'll also supply the data directly when we create the ACI object this time, instead of calling the `update` method afterwards.
```{r dtaci}
result_dtaci <- aci(
  Y[t_star:length(Y)],
  predictions[t_star:length(Y)],
  method = "DtACI", 
  alpha = 0.9
)
```

```{r dtaci_summary}
summary(result_dtaci)
```

```{r dtaci_plot}
plot(result_dtaci)
```

```{r dtaci_plot_zoom}
plot(result_dtaci, index = 200:300)
```

If we plot the results from both the AgACI and the DtACI methods, we see that they yield quite similar prediction intervals.
```{r comparison_plot}
plot(result$Y[200:300], ylim = c(30e3, 85e3))

# AgACI
lines(result$intervals[200:300, 1], col = "darkred")
lines(result$intervals[200:300, 2], col = "darkred")

# DtACI
lines(result_dtaci$intervals[200:300, 1], col = "blue")
lines(result_dtaci$intervals[200:300, 2], col = "blue")

legend("topright", legend = c("AgACI", "DtACI"), fill = c("darkred", "blue"))
```
